Approximation as Differentiation notes

### 2025-02-21 notes/definitions.tex
Bilinearity.

A category $C$ is \emph{$\CMon$-enriched} if every hom-object $\Hom{C}{A}{B}$ is a commutative monoid with a
\emph{zero} morphism $\zero_{A,B}$ and addition of morphisms $+_{A,B}$ as the commutative monoid operations,
and composition is a morphism $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$,
i.e.~satisfies

\begin{salign*}
(f + g) \comp h &= (f \comp h) + (g \comp h) \\
h \comp (f + g) &= (h \comp f) + (h \comp g)
\end{salign*}

>>>>

A category $C$ is \emph{$\CMon$-enriched} if every hom-object $\Hom{C}{A}{B}$ is a commutative monoid with a
\emph{zero} morphism $\zero_{A,B}$ and addition of morphisms $+_{A,B}$ as the commutative monoid operations,
and composition is a family of morphisms $\Hom{C}{B}{C} \tensor \Hom{C}{A}{B} \to \Hom{C}{A}{C}$ in $\CMon$,
i.e.~satisfies

\begin{salign*}
f \comp \zero = f = \zero \comp f
\end{salign*}
\begin{salign*}
(f + g) \comp h &= (f \comp h) + (g \comp h) \\
h \comp (f + g) &= (h \comp f) + (h \comp g)
\end{salign*}
